Position: Stop Making Unscientific Inflated AGI Claims

### 2024-05-27 body.tex

Finally, another recent work closely aligned with the position we present here is~\ref*{schaeffer2024emergent}.

>>>>

Finally, another recent work closely aligned with the position we present here is~\ref*{schaeffer2024emergent}. The authors demonstrate that the apparent emergent abilities of large language models may be driven by a choice of evaluation metrics, rather than some fundamental property that is intrinsic to this family of models. Their work highlights the need for rigorous testing and benchmarking of LLMs, which we also point to in this work albeit in a slightly different methodological context.

### 2024-05-27 main.tex

% The \icmltitle you define below is probably too long as a header.
% Therefore, a short form for the running title is supplied here:
\icmltitlerunning{Position: Inflated AGI Claims Require Strong Tests and Dovelation}

@@

\twocolumn[
\icmltitle{Position: Inflated AGI Claims Require Strong Tests and Dovelation \raisebox{-6pt}{\includegraphics[scale=0.09]{dove_1f54a-fe0f.png}}}

>>>>

% The \icmltitle you define below is probably too long as a header.
% Therefore, a short form for the running title is supplied here:
\icmltitlerunning{Position: Stop Making Unscientific Inflated AGI Claims}

@@

\twocolumn[
\icmltitle{Position: Stop Making Unscientific Inflated AGI Claims}
